Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add James placeholder to mets
Add obs to methods

\subsection{Observations}\label{ssec:obs}

>>>>

\subsection{Observations}\label{ssec:obs}
We make use of two observational data sets. First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}. We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4. These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's. This results in a sample of 54,777 stars. We use Fe to track total metallicity and Mg alone as an $\alpha$-element \red{TODO: add any additional details}.

We then further considered a dataset of stellar ages from the APOKASC2 catalog \citep{2018ApJS..239...32P}. This uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages. We cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1868 stars.

\subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
James inserts his bullshit
